%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\RequirePackage{fixltx2e}
\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{hernán}{morales}{full-stack developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Calle 25 no. 506
La Plata (1900), Buenos Aires
Argentina
~
+54 (221) 479-7117
~
\href{mailto:hernan.morales@gmail.com}{hernan.morales}
\href{http://80738163270632.blogspot.com/}{http://80738163270632}
\href{http://biosmalltalk.blogspot.com/}{http://biosmalltalk}
\href{https://www.linkedin.com/in/hernanm}{li://hernanm}
\href{https://github.com/hernanmd}{gh://hernanmd}
\section{languages}
spanish mother tongue
english advanced
français, lu bien, parlé et écrit régulier
\section{programming}
{\color{red} $\varheartsuit$} Smalltalk
Bash, R, Python, Solidity, C++, SPARQL
GoLang, CSS3 \& HTML5
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2019}
{Decentralized Applications (Dapps)}
{University at Buffalo and The State University of New York}
{Grade Achieved: 94.9\%}

%------------------------------------------------

\entry
{2018}
{Smart Contracts}
{University at Buffalo and The State University of New York}
{Grade Achieved: 88.0\%}

%------------------------------------------------

\entry
{2014}
{R Programming}
{Johns Hopkins University.}
{Grade Achieved: 88.8\%}

%------------------------------------------------

\entry
{2014}
{Bioinformatics: Introduction and Methods}
{Peking University}
{Grade Achieved: 95.2\% with Distinction.}
%------------------------------------------------

%------------------------------------------------

\entry
{1996--2003}
{Computer Science (4th Years)}
{Facultad de Informática. UNLP, Argentina}
%------------------------------------------------


\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\subsection{Full Time}

\begin{entrylist}

%------------------------------------------------

\entry
{2010--Now}
{CONICET}
{La Plata, Buenos Aires}
{\emph{Developer @ IGEVET. Institute of Veterinary Genetics} \\
Requirements engineering, project management, 
coding, documentation and testing. Common tasks in my work are data engineering
for biologists and geneticists, determine software and hardware needs, specify and evaluate
technology brands and vendors \\
Detailed achievements:
\begin{itemize}
\item Created BioSmalltalk, the first pure-objects library for Bioinformatics.
\item Applied Data Science with R and Python scripting.
\item Built Institutional front-ends (HTML, CSS3, PHP, Smalltalk). 
\item Developed HPC cluster from scratch (Qlustar, Singularity, Galaxy).
\item Developed Phylogeography text-mining system, Microarray and NGS big data sets.
\end{itemize}}

\entry
{2006--2009}
{CONICET}
{Ciudad Autónoma de Buenos Aires, Argentina}
{\emph{Developer @ CAICYT} \\
Bibliographic Management System Project. First implementation of FRBR-oo reference model in Smalltalk, including major improvements. Experience with expertise visualization, website usability and optimization. Integration of multiple Information Systems (from National ISIS Database). Open-sourced libraries and toolkits. Experience with GemStone/S OODB and Seaside Web Framework.}


%------------------------------------------------

\entry
{2004-2005}
{Reyes Infográfica}
{Remote Work}
{\emph{Developer} \\
Technology Project for 3-D Virtual Fashion Works. Developement and implementation of an ANSI high-performance Smalltalk dialect, an interface with a propietary 3D engine and several frameworks, including GUI and navigational tools.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}

%------------------------------------------------

\entry
{2016}
{INNOVAR 2016}
{Ministerio de Ciencia, Tecnología e Innovación Productiva. Argentina}
{For Applied Research in the Design of SNP Microarray “ArBos1”.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{communication skills}

\begin{entrylist}

%------------------------------------------------

\entry
{2016--2017}
{Oral Presentations}
{IGEVET, Argentina}
{As part of the annual semminary for researchers, I gave speaks about state of Information Technology Infrastructure at the Institute.}

%------------------------------------------------

\entry
{2011}
{Oral Presentation}
{XL Genetics National Argentine Conference. Corrientes, Argentina}
{Introduction to Bioinformatics Programming}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} software design, project management, web apps, IT security 
\textbf{personal:} guitar player, argumentation theory, tango dancing.

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}

\printbibsection{article}{article in peer-reviewed journal} % Print all articles from the bibliography

\begin{entrylist}

\entry
{2018}
{Genomic structural diversity in Criollo Argentino horses: analysis of copy number variations}
{Accepted}
{Gene}

\entry
{2017}
{Evidence of positive selection in the BoLA region of Brangus cattle}
{DOI: 10.1017/S1751731117001380}
{Animal Journal}

\entry
{2016}
{DNA profile of dog feces as evidence to solve a homicide}
{DOI: 10.1016/j.legalmed.2016.08.002}
{Legal Medicine 22:54-57}

\entry
{2014}
{Foreign meat identification by DNA breed assignment for the Chinese market}
{DOI: 10.1016/j.meatsci.2014.07.028.}
{Meat Science 98(4):822–827}

\entry
{2013}
{BioSmalltalk: a pure object system and library for bioinformatics}
{DOI: 10.1093/bioinformatics/btt398}
{Bioinformatics}

\entry
{2007}
{Introduction to object-oriented databases with db4o, .NET C\# \& Java}
{DOI: 10.1093/bioinformatics/btt398}
{Solo Programadores n. 150 (June 2007)}


\end{entrylist}

\printbibsection{book}{books} % Print all books from the bibliography

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" but not containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=bibheading]
\end{refsection}

\begin{refsection} % This is a custom heading for those references marked as "inproceedings" and containing "keyword=france"
\nocite{*}
\printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=bibheading]
\end{refsection}

\printbibsection{misc}{other publications} % Print all miscellaneous entries from the bibliography

\printbibsection{report}{research reports} % Print all research reports from the bibliography

%----------------------------------------------------------------------------------------

\end{document}